\chapter{Research Questions} \label{chap:research-questions}


\section{Predicting a stock market index's direction} \label{predicting_direction_question}
\textbf{Question} Is it possible to accurately predict a stock market index's (S\&P 500) direction for
the following day with an artificial intelligence model?\\
\textbf{Sub Questions}
\begin{itemize}
    \item If so, what is the accuracy of the model?
    \item If not, what limitations affected the model to cause it to be inaccurate?
    \item Can the findings of this question be used to prove/disprove the efficient market hypothesis?
\end{itemize}
\textbf{Importance} The findings from this research question will have significant impact in making
investment and trading decisions for participants of the market, potentially giving indicators of
when to buy / sell into the stock market in order to outperform the market. Furthermore, depending
on the accuracy of the model, it may be able to be used as evidence for or against the efficient
market hypothesis.

\section{Optimal amount of historical data as input} \label{optimal_historical_question}
This question assumes that it is at least somewhat possible to accurately predict the stock market index's
direction/price based on literature review and other studies.\\
\textbf{Question} How do different lengths of time as historical data of input features affect the model?\\
\textbf{Sub Questions}
\begin{itemize}
    \item What is the ideal length of time of historical data of input features to be used?
    \item What are potential reasons for this length of time being the most useful?
\end{itemize}
\textbf{Importance} The findings from this research question will allow optimal algorithms /
models to be created in order to avoid wasting computational time that may cause the model to 
not improve, or even decrease in accuracy. Furthermore, this will be of help to participants of
the market to make better informed manual decisions by understanding which time horizons to look
at.

\section{Most important input features} \label{most_important_features_question}
This question assumes that it is at least somewhat possible to accurately predict the stock market index's
direction/price based on literature review and other studies.\\
\textbf{Question} What are the most important input features that affect the model?\\
\textbf{Sub Questions}
\begin{itemize}
    \item How much do each of these input features contribute to the model?
    \item Do any of the input features identified have negligible impact to the model?
    \item What are the potential reasons these features do / do not impact the model?
\end{itemize}

\textbf{Importance} The findings from this research question will allow optimal algorithms /
models to be created in order to avoid wasting computational time that may cause the model to 
not improve, or even decrease in accuracy. Furthermore, this will be of help to participants of
the market to make better informed manual decisions by understanding which factors to look
at.